\documentclass[11pt,courier]{navymemo}

%\newcommand{\myroot}{../..}
%\usepackage{\myroot/ew305}
%incompatible for some reason?

\newcommand{\usnaCourseNumber}{EW282D}
\newcommand{\usnaCourseName}{Biomechanics}
\newcommand{\usnaInstructor}{Assistant Professor D Evangelista}
\newcommand{\usnaInstructorShort}{D Evangelista}
\newcommand{\usnaCourseSection}{0451}
\newcommand{\usnaCourseTerm}{Spring 2020}
\newcommand{\Google}{Google}
\newcommand{\GoogleClassroom}{Google Classroom}

\author{\usnaInstructor}
\title{\usnaCourseNumber\ Course Policy}
\navysubj{Course policy for \usnaCourseNumber\ (\usnaCourseName)}
\navyfiling{1531}
%\navyserial{16-0001}
\date{\today}
%\navymarking{UNCLASSIFIED}

\usepackage{designature}
%\usepackage{siunitx}
\usepackage[colorlinks=true,urlcolor=blue]{hyperref}
%\usepackage{gitinfo2}

\usepackage{multirow}
\usepackage{xcolor,colortbl}
\usepackage{hhline}

\begin{document}
\makedateblock{}

\MEMORANDUM{}

\begin{navyletterheader}
\navyfrom{\usnaInstructor}
\navyto{\usnaCourseNumber\ Section \usnaCourseSection}
\navyskip{}%

\navysubjline{}
\navyskip{}%
\navyref{refa}{ACDEANINST 1531.58 (Administration of Academic Programs)}
\navyref{refb}{USNAINST 1531.53B (Policies Concerning Graded Academic Work)}
\navyref{refc}{SECNAVINST M-5216.5 (Department of Navy Correspondence Manual)}
\navyref{refd}{USNAINST 1610.3H (Brigade Honor Program)}
\navyref{refe}{COMDTMIDNINST 1752.1E (Sexual Assault Prevention and Response Program)}
%\navyskip{}%
\navyencl{encl1}{Syllabus, \usnaCourseNumber\ (\usnaCourseName), \usnaCourseTerm}
\end{navyletterheader}

\section{} Per reference~(\ref{refa}), this memorandum sets forth my course policy for the \usnaCourseTerm\ session of \usnaCourseNumber\ (\usnaCourseName). This information supplements the basic guidance provided in references~(\ref{refa}) through (\ref{refe}) and enclosure~(\ref{encl1}). \usnaCourseNumber\ may meet with EW496 (Biomechanics Independent Research for upperclass) but the assignments will differ.
 
\section{Course objectives} The objective of this course is to introduce underclass to methods used in comparative biomechanics and biomedical engineering.  At the end of the course, a student should be able to:
\begin{itemize}
\setlength\itemsep{0em}
\item Direct observe and sketch specimens using basic scientific illustration techniques.
\item Obtain quantitative measurements of kinematics of biological movement. 
\item Obtain quantitative measurements of external applied forces and moments, and/or internal reactions in biological systems.
\item Obtain basic electrophysiological measurements.
\item Have a basic understanding of the use of physical, analytical, and computational models in biology.
\item Ask biological questions, generate and test hypotheses, as demonstrated in a pilot study related to biomechanics.
\item Care for biological specimens. 
\end{itemize} 

This course is inspired by UC Berkeley IB135L (Mechanics of Organism Lab), but is arranged similar to USNA EW281C/EW282C (School of Drones) and targeted at underclass specifically to build skills used in further USNA biomechanics research and capstone projects. 

\section{Biomechanics seminar} Students in \usnaCourseNumber\ are \textbf{highly encouraged} to attend and/or present at the weekly USNA Biomechanics Seminar Series. 
 
\section{Grading policy} The interim and final course grades will be based on the following approximate grade weights:
\begin{table}[h]
\begin{center}
\begin{tabular}{|p{3in}|p{0.5in}|}\hline
Demonstration of lab techniques & 30\% \\\hline
Level of knowledge about biomechanics & 30\% \\ \hline
Progress towards an independent research project & 30\% \\ \hline
Professionalism (lab neatness, scientific curiosity, interest and effort) & 10\% \\ \hline
\end{tabular}
\end{center}
\end{table}

We do not plan any written exams, but may have quizzes on technical material, knowledge checkouts, or practical factors for operating gear. We may require you to complete a qualification card to document that you are capable of safely operating biomechanics lab gear.

\section{Course materials}
Whenever possible, course materials including homework assignments are available via \GoogleClassroom. There is no required textbook for \usnaCourseNumber; we will provide notes and access to the EW485E (Comparative Biomechanics) course materials. Optional text to be placed on reserve at Nimitz Library: Vogel, S (2008) \textbf{Comparative Biomechanics}, Princeton University Press.  

\section{Coursework}
Most work will be completed during the two hour lab session, but some analysis or background research outside of class will be necessary.
\begin{itemize}
\item You are encouraged to read up on techniques and complete any pre-lab before coming to lab.
\item You are highly encouraged to apply the techniques you are learning to specific organisms, systems, or activities of personal interest to you!
\item Indulge your curiosity!
\end{itemize}

\section{Classroom and laboratory hardware}
We will meet Fridays, 3/4 period, in Maury 226. This classroom is shared with other lab groups (e.g. Jaramillo Group) and must be kept neat. Hardware is used for active midshipman, capstone, and professor academic research and is needed for future offerings of EW282D, EW485E, etc so please respect it. Drinks are permitted in closed containers. 

\section{Devices}
Use of phones and internet unrelated to class is prohibited, however, you may choose to participate in School of Drones related social media (e.g. \texttt{@NavyBiomech}, hashtags \texttt{\#gonavy \#biomechanics} as part of our STEM outreach. 

\section{Diversity and conduct}
Biology is a science of diversity best done as a team. Biology is sometimes done in the field or in isolated sites where the team must work closely and with respect for each other. Per reference~(\ref{refd}), an important aspect in the implementation of the Naval Academy’s mission is to develop selfless leaders who value diversity and create an ethical command climate through their example of personal integrity and moral courage. If this attribute remains a common goal for each Midshipman, faculty and staff, all members of the team will be treated with dignity and respect. Additionally, the Brigade and classroom climate will not tolerate violence against others, reducing the potential risk of sexual assault.

\section{Section leader, absent/late instructor}
The section leader is responsible for taking attendance and calling the class to attention at the beginning and end of the class period..  In the event that the course instructor is more than ten minutes late for class, the section leader will report to the department office (Maury 306) for further instruction. If there is no packet, and no further instructions are available from the department educational technician, the remainder of the class should be used to work on the assigned project or homework assignment.  Class is not canceled.
 
\section{Office Hours and Extra Instruction (EI)} Midshipmen are encouraged to arrange EI as needed (appointments encouraged).  I am teaching EW309 (Guided Design Experience) MWF1-4; EW282C (School of Drones) R5-6; and EW282D (Biomechanics Lab) F3-4. Tuesday is typically used for research but is available by appointment. There may be a Labrador retriever guide dog puppy in training at my office; if this is an issue for you I can make alternate arrangements. 
\begin{table}[h]
\begin{center}
\begin{tabular}[h]{| c | c | c | c | c | c | c |}
\hline
\bf Period & \bf I & \bf II & \bf III & \bf IV & \bf V & \bf VI\\
\hline
MON & \multicolumn{2}{c|}{\cellcolor{orange}EW309 lab} & \multicolumn{2}{c|}{\cellcolor{orange}EW309 lab} & &\\
\hline
TUE & \multicolumn{6}{c|}{\cellcolor{yellow}Research / by appointment only}\\
\hline
WED & \multicolumn{2}{c|}{\cellcolor{orange}EW309 lab} & \multicolumn{2}{c|}{\cellcolor{orange}EW309 lab} & &\\
\hline
THU & & & & \multicolumn{2}{c|}{\cellcolor{orange}EW282C lab} & \\
\hline
FRI & & \multicolumn{2}{c|}{\cellcolor{orange}EW282D lab} & & & \\
\hline
\end{tabular}
\end{center}
\end{table}

\noclosing{}\\
%\signspace{}
\noindent\hspace*{4in}\includesignature{}
\signature{D Evangelista}
\sendertitle{Assistant Professor}

\noindent\hspace*{4in}{207 Maury Hall}\\
\hspace*{4in}{(410) 293-6132}\\
\hspace*{4in}{\href{mailto:evangeli@usna.edu}{evangeli@usna.edu}}






\copyto{}
File\\
Course coordinator


% record note
\navyrecordnote
\thispagestyle{empty}

\navyrecordnotedistribution{%
Evangelista\\%
Jaramillo\\
LCDR Chapman}%
%\navyrecordnoteconcurrences{%
%\navyrecordnoteconcurrence{08K}
%\navyrecordnoteconcurrence{08I}}

\navyrecordnotesubjline

\section{}  This memo provides course policie \usnaCourseTerm\ \usnaCourseNumber.

\section{}  The policies here are adapted from those from EW282C, merged with ideas from Berkeley IB135L.

%\section{} File information: \gitMark
\end{document}


