\documentclass{exam}

\newcommand\myroot{../..}
\usepackage[quiz]{\myroot/course}

\title{Course Syllabus, \usnaCourseTerm}
\author{\usnaInstructorShort}
\date{\today}

\begin{document}
\maketitle

\begin{questions}
%1. Organizational meeting, admin, Navy flight clearances, Part 104, and AMA. Flight time with available airframes. 
\question \printdate{\courseWeekOne} -- \textbf{Introductions and organizational meeting.}

\question \printdate{\courseWeekTwo} -- \textbf{Kinematics.} High speed cameras. Digitization. Estimating angles, velocities, and accelerations. Single camera calibration. Illumination. 

\question \printdate{\courseWeekThree} -- \textbf{Kinematics.} OptiTrack (TBD). Introduction to 3D camera calibration. Markers, illumination, and scale. 

\question \printdate{\courseWeekFour} -- \textbf{Kinematics.} Time lapse. Also thermal imaging. 

\question \printdate{\courseWeekFive} -- \textbf{Kinematics in the field.} Use of multiple GoPro cameras and 3D camera calibration. Introduction to use of drones. 

\question \printdate{\courseWeekSix} -- \textbf{Seeing like a biologist.} Direct observation. Scientific illustration techniques. Naturalist journals. Low stress for 6 weeks. 

\vspace{1em}
\hrule
\vspace{1em}

\question \printdate{\courseWeekSeven} -- \textbf{Dynamics.} Measuring forces via various means; spring scales; force transducers; force plates.

\question \printdate{\courseWeekEight} -- \textbf{Dynamics.} Measuring forces and moments on objects in fluids (TBD, visit Hydro Lab?) or measuring material properties (TBD). Use of physical models. 

\question \printdate{\courseWeekNine} -- \textbf{Surface electromyography.} 

\question \printdate{\courseWeekTen} -- \textbf{Electrophysiology continued.} Muscle stimulation, twitches and tetanuses. TBD: visit to Human Performance Lab, treadmill kinematics and energetics, VO$_2$. 

\question \printdate{\courseWeekEleven} -- \textbf{Modeling and simulation in biology.} Brief introduction to \Matlab, OpenSim, or Python. Use of physical models. 

\question \printdate{\courseWeekTwelve} -- \textbf{Seeing like a biologist.} Dissection; measurement issues with live or dead tissue. Low stress for 12 weeks.

\vspace{1em}
\hrule
\vspace{1em}

\question \printdate{\courseWeekThirteen} -- Advanced topics or guests. Project TBD.

\question \printdate{\courseWeekFourteen} -- Advanced topics or guests. Project TBD.

\question \printdate{\courseWeekFifteen} -- Advanced topics or guests. Project TBD.

\question \printdate{\courseWeekSixteen} -- \textbf{Demo projects.} 
\end{questions}

\textbf{No final exam, no final project written report.}

TBD: Visits to Human Performance Lab, Hydro Lab, Wind Tunnel, materials lab; Zoo, Aquarium, or NMNH MO.
\end{document}







